Comparing microbial communities with OptiFit: a fast method for fitting sequences to existing OTUs

### 2021-03-11 docs/slides/2021-03-11_bistro.Rmd
Adjust snakemake links

.footnote[
[snakemake.readthedocs.io](snakemake.readthedocs.io)
]

@@

.center[
<img src="https://raw.githubusercontent.com/snakemake/snakemake/f55801bfabfb916f77fa4ec8f9eb0667e5c8a92e/docs/project_info/img/idea.png" width="900" />
]

.footnote[
[snakemake.readthedocs.io](snakemake.readthedocs.io)
]

>>>>

.footnote[
[snakemake.readthedocs.io](https://snakemake.readthedocs.io)
]

@@

&nbsp;

.center[
<img src="https://raw.githubusercontent.com/snakemake/snakemake/f55801bfabfb916f77fa4ec8f9eb0667e5c8a92e/docs/project_info/img/idea.png" width="1000" />
]

.footnote[
[snakemake.readthedocs.io](https://snakemake.readthedocs.io)
]
